\cvsection{Projects}

\begin{cventries}

  \cventry
    {Food Ordering & Delivery Microservices Platform}
    {\href{https://github.com/nmdra/CraveDrop}{CraveDrop \faGithub}}
    {SLIIT}
    {Jan. 2025 -- May 2025}
    {
      \begin{cvitems}
        \item {Built a Kubernetes based microservices backend for restaurant order management with RabbitMQ for messaging and Docker Compose for deployment.}
        \item {Implemented scalable service communication and CI workflows using GitHub Actions.}
        \item {Technologies: Kubernetes, Docker, PostgreSQL, RabbitMQ}
      \end{cvitems}
    }

  \cventry
    {Snippetbox: Go based Code Snippet Manager}
    {\href{https://github.com/nmdra/snipbox}{Snipbox \faGithub}}
    {Personal Project}
    {Sep. 2024 -- Dec. 2024}
    {
      \begin{cvitems}
        \item {Developed with Docker based hot reload, production ready image with MySQL support, and TLS security.}
        \item {Technologies: Go, Docker, Docker Compose, MySQL}
      \end{cvitems}
    }

  \cventry
    {Farm-to-Table E-Commerce Platform}
    {\href{https://github.com/nmdra/FarmCart}{FarmCart \faGithub}}
    {SLIIT}
    {June 2024 -- Nov. 2024}
    {
      \begin{cvitems}
        \item {Created a scalable platform connecting farmers and consumers with CI/CD pipelines and containerized workflows.}
        \item {Technologies: React, TailwindCSS, MongoDB, Docker, GitHub Actions}
      \end{cvitems}
    }

  \cventry
    {Hotel Booking Management System}
    {\href{https://github.com/nmdra/Reservify/}{Reservify \faGithub}}
    {SLIIT}
    {Oct. 2023 -- Nov. 2023}
    {
      \begin{cvitems}
        \item {Designed a hotel reservation system with room availability, bookings, and admin features.}
        \item {Technologies: PHP, MySQL, JavaScript, CSS}
      \end{cvitems}
    }

  \cventry
    {Other Personal Projects}
    {}
    {}
    {}
    {
      \begin{cvitems}
        \item {\href{https://github.com/nmdra/K8s-Learn}{\textbf{Kubernetes HomeLab} \faGithub} — Explored deployments, services, and configs.}
        \item {\href{https://github.com/nmdra/Ansible-Learn}{\textbf{Ansible HomeLab} \faGithub} — Practiced infrastructure automation with provisioning examples.}
        \item {\href{https://github.com/nmdra/RabbitMQ-Learn}{\textbf{RabbitMQ-Learn} \faGithub} — Hands-on with messaging patterns and exchanges.}
        \item {\href{https://github.com/nmdra/gRPC-Learn}{\textbf{gRPC Services} \faGithub} — Built unary and streaming RPC services in Go.}
        \item {\href{https://github.com/nmdra/Go-Mini-Projects}{\textbf{Go-Mini-Projects} \faGithub} — Demonstrated concurrency, APIs, and file handling.}
        \item {\href{https://github.com/nmdra/Redis-Learn}{\textbf{Redis Examples} \faGithub} — Explored caching and pub/sub messaging.}
      \end{cvitems}
    }

\end{cventries}
