%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[11pt, a4paper]{awesome-cv}

\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

\colorlet{awesome}{awesome-red}
\setbool{acvSectionColorHighlight}{true}
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

% Personal Info
\name{Nimendra}{Dilshan}
\position{Software Engineering Undergraduate}
\address{Kurunegala, Sri Lanka}
\mobile{(+94) 767067343}
\email{nimendradharmasiri@gmail.com}
\homepage{blog.nimendra.xyz}
\github{nmdra}
\linkedin{nimendra}
% \twitter{@nimendra_}
% \quote{``Keep learning, Train your own model."}

% Letter Info
\recipient
  {Hiring Manager}
  {IFS\\Global Headquarters}
\letterdate{\today}
\lettertitle{Application for DevOps/Site Reliability Engineering Internship}
\letteropening{Dear Hiring Manager,}
\letterclosing{Sincerely,}
\letterenclosure[Attached]{Resume}

\begin{document}

\makecvheader
\makecvfooter
  {\today}
  {Nimendra Dilshan~~~·~~~Cover Letter}
  {}
\makelettertitle

\begin{cvletter}

\lettersection{About Me}

I am a third-year Software Engineering undergraduate with a strong passion for DevOps and Site Reliability Engineering (SRE). I have been developing my skills in building automated, scalable, and observable systems through academic projects and personal learning. I have hands-on experience with containerization using Docker and orchestration with Kubernetes. I also have intermediate knowledge of building CLI tools using Go and frequently use Bash scripting to automate my day-to-day workflows. My experience includes implementing CI/CD pipelines with GitHub Actions, provisioning infrastructure using Terraform and Ansible, and practicing core SRE principles such as monitoring, alerting, and reducing toil through automation.

\lettersection{Why This Role?}

I’m excited about the opportunity to join a team where I can apply and grow my DevOps skills while tackling real-world SRE challenges. This internship closely aligns with my interests in building and maintaining infrastructure that supports fast, reliable, and secure software delivery. I’m particularly drawn to environments that embrace infrastructure as code, continuous delivery, and internal developer tooling—areas where I can contribute through Dockerized workflows and scalable system architecture.

\lettersection{Why Me?}

In my recent projects, I have built CI/CD pipelines to streamline deployments, automated provisioning tasks using Terraform, and created monitoring setups to track system health and reliability. My proactive approach to learning and my ability to quickly adapt to new tools and challenges make me a strong candidate for this internship. I’m eager to bring my skills and enthusiasm to your team and continue developing as a DevOps/SRE engineer.

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter information
\makeletterclosing

\end{document}
